\section {History of Capacitors}

\subsection{Comments}
\begin{enumerate}
    \item You talk about the different types of MLCCs but are not very clear as to how the differences are achieved.
    \item You said very little about electrolytics in your discussion and the latest are low-voltage supercapacitors.
    \item Need to add in some discussion on titanium capacitors.
\end{enumerate}

\subsection{History}
This section will chronolog the history of capacitors. It will link various introductions in the technology to advances in industry, and it will map the driving forces behind capacitor development.

Capacitors have their origin in the invention of the Leyden jar by Peter van Musschenbroek of Leiden University in 1745.\cite{empLight} Before this point, scientists were able to generate static electricity through electrostatic machines, but had a very limited ability to store this electrical energy. 
\cite{ieee_hist} 
The most common design for the Leyden jar was to use a glass jar with metal foil lining the inside and out. The inner foil was typically charged via an electrostatic generator, while the outer foil was connected to ground. The charge would stay on the metal foil until a short or small resistance was connected between them. Charge could be stored this way, allowing scientists and showmen, to use greater amounts of current than they could generate at any one moment.
Since the Leyden jar, many different types of capacitors have risen and fallen in prominence in the market. This section will cover the historical introduction of some of the major types.

In 1876 Fitzgerald introduced wax impregnated paper dielectric capacitors with foil electrodes.\cite[ch.~11]{dumInv} \cite{learn_caps} They were typically used for power supply filtering in radios. By the early 1920s, they existed as tubes encapsulated in plain, Bakelite cardboard, with bitman sealing the ends and waxed paper as a dielectric.\cite[ch~3]{dumInv}
Paper capacitors were upgraded to impregnated paper capacitors, which used paper that was soaked in mineral oil. They were interleaved with metal foil and then rolled to make the capacitor.\cite[ch.~8.2.1.1]{poorIntro} During WW2, paper capacitors were upgraded with metal-cased tubes with a rubber end.\cite[ch.~8.1]{poorIntro} These metalized paper capacitors were constructed similarly with the improvement that one side of the paper dielectric was sprayed with metal.\cite{hist_cerFilt}

Karol (Charles) Pollak discovered the principle of the electrolytic capacitor in 1886 while he was researching the anodizing of metals, and received a patent for the borax-solution aluminum electrolytic capacitor in 1897.  
In 1936 Cornell-Dubilier opened a factory to produce aluminum electrolytic capacitors. 
After the start of WW2, increased funding and effort was applied to the cause of electrolytic capacitors and techniques such as "etching and pre-anodizing" greatly increased their reliability.\cite{deis_hist}\cite{wiki_elec}

The science of electrolytic capacitors was extending into what is now know as electrochemical capacitors in 1957 by GE. This technology, also known as electric double layer capacitors, was not commericallized until NEC liscenced Standard Oil's patent in 1978.\cite{electrochem_intro} This "supercapacitor" formed the basis of today's EC capacitors. They are characherized by a large capacitance in the range of kilo farads, but with a working voltage of only 2.7V.\cite{electrochem_intro} Some of today's typical applications for EC capacitors are in battery replacement, electric vehicle, and regenerative breaking.

\nocite{hh}
\nocite{capGuide_mica}
M. Bauer of Germany invented the mica capacitor in 1874. The original mica capacitor was a ``clamped'' style capacitor, which was used through the 1920s\cite{wiki_mica} and then replaced by silver mica capacitors.\cite{learn_caps}
Mica's inherent inertness and reliability allowed for extreme reliability and efficiency in a packaged capacitor.\cite{tedds_mica} Mica capacitors were heavily used in the radio industry due to their superb stability at RF frequencies and their physical robustness.\cite{radio_mica}
Capacitors created with mica allowed a compartively smaller product\cite[f.~37-41]{dumInv} which had the ability to survive shock from weapons better than its glass counterpart. Consequently, mica capacitors began to be produced in large quantities during WWI.

In light of mica supply chain problems and the emergence of ceramic capacitors during WW2, mica capacitors fell from prominence to a niche market.\cite[Ch 3, Sec II]{cerMaterials}

The first glass ceramic dielectric capacitor was the Leyden jar. While this early capacitor was used mainly for scientific experiments, commercial glass capacitors came later. 
Glass tubular capacitors, known as Moscicki tubes, appeared in 1904 and were used in Marconi's experiments in wireless transmission. They continued to be used in wireless communication until about WWI. \cite[p.~102]{dumInv}

Scientists in Germany created the first steatite ceramic capacitor in 1920. \cite[Ch 3 Sec II]{cerMaterials} \cite{cerDie} Also known as talc, this ceramic capacitor variant was able to closely match the temperature coefficient of mica.\cite{steatite_hf} Rutile was later introduced into ceramic capacitor technology. It was able to produce a dilectric constant of 10 times that of steatite, but the two were typically blended to get a better temperature coefficient. 

A ceramic composition with barium titanate (BaTiO3) was first discovered in 1941. Barium titanate was quickly found to be able to exhibit a dielectric constant over 1000; an order of magnitude greater the best at this time (rutile - $Ti0_2$). It was not until 1947, that barium titanate appeared in its first commercial devices, phonograph pickups.\cite{piezCer}\cite{hist_cerFilt}\cite[Ch 3 Sec III]{cerMaterials} Barium titanate is still used today in certain types of multi-layer ceramic capacitors.

Thanks to the semiconductor industry, MLCCs grew to dominate the capacitor market and by 1979, AVX alone reached $\$95$ million in MLCC sales.\cite{avx_hist}
MLCCs are divided up into three classes. Class 1 type MLCCs are known for their extremely good temperature characteristics. COG/NPO types can have 0-30ppm/$^o$C. These capacitors are typically made by combining $TiO_2$ with additives in order to adjust its temperature characteristics\cite{intro_cerCaps}. Additionally, class 1 ceramics have comparatively poor volumetric efficiency, and will tend to come in larger packages than class 2 ceramics of the same capacitance value. Class 2 types typically have worse temperature coefficients than type 1 types, but they have a much higher volumetric efficiency. They are constructed with a ferroelectric base material, typically Barium Titanate.\cite{intro_cerCaps}. Class 2 ceramic capacitors are the most common type of ceramics used. Class 3 types have very high capacitance, but a working voltage of several volts.\cite{hist_cerFilt}\cite[Ch 3 Sec VI]{cerMaterials}\cite{atCer_tempco}. They were originally developed as a potential replacement for liquid electrolytics, but have fallen out of favor due to the advances in Class 2 ceramics to the point where the gap between these two in terms of maximum capacitance is no longer viable\cite{wiki_cer}.

Bell labs invented the first solid tantalum capacitor in 1956. They created it in conjuncture with, and for, transistors.\cite[f.~56-64]{dumInv} Tantalum capacitors typically have better characteristics than aluminum electrolytics, but have a lower maximum capacitance and working voltage.\cite{learn_caps}
Sprague patented the first commercially viable solid tantalum capacitor in 1960. It offered an increased capacitance per unit volume and greater reliability.\cite{charTant} In the 1970s, Sprague released the first surface mount tantalum capacitor.\cite{spragueHist}
One of the historical problems with tantalum capacitors has been a limited and volatile supply of tantalum in the world market. 
As a result of a price spike around 1980, manufacturers created finer grain tantalum powders. This allowed a unit to be made with less overall tantalum, reducing price and package size.\cite[ch~3.1]{tantMis}
Over time, this volatility has decreased the popularity of tantalum capacitors and has led to a desire for a suitable replacement.

