\section{Todo}

\subsection{Misc}
\begin{itemize}
    \item Add some numbers to the abstract.
    \item Update tab on first paragraph in sections.
    \item Get rid of all LaTex warnings.
    \item Put date instead of TBD on title page.
    \item Combine TOF and TOT onto same page.
    \item Fix no comma in bibliography when multiple authors are present (ie: \cite{absCircuit}).
    \item Expand \nameref{sec:abstract} by including some numbers.
\end{itemize}

\subsection{MATLAB}
\begin{itemize}
    \item Combine iteration scripts into a single unit.
\end{itemize}

\subsection{Parameters}
\begin{itemize}
    \item Add angle marker to loss tangent image.
    \item Add model for leakage resistance.
\end{itemize}

\subsection{Regression}
\begin{itemize}
    \item Include some discussion on J. Miller's modeling techniques for supercapacitors.
    \item Either add more models or don't say that you will in the intro
    \item Levy + err figures have 3 figures in a row and split a sentence.
    \item What model would be useful for modeling titanium electrolytic capacitors.
    \item Tie this section into the circEx to say that we are modeling from emperical data.
    \item Say that the 6-term model is a good place to stop for this thesis. Validating and updating it will be in the future work section. We may not even need a 6-term model.
\end{itemize}

\subsection{Schematic Explanation}
\begin{itemize}
    \item Update discussion on leakage measurements.
    \item Say that this is a conceptual design and mention the parts that are based off of work that I did with SE.
    \item Expand the overview before launching into the circuitry.
    \item Create a flow chart for the schematic.
    \item Plot the safe operating area with Matlab.
    \item Talk about why this phase measurement technique was chosen over others and their comparable accuracy.
    \item Expand explanation on the current booster.
\end{itemize}

\subsection{Conclusion}
\begin{itemize}
    \item Expand this section.
\end{itemize}

