\section {Measurement Circuitry}
\label{sec:measCirc}
\renewcommand{\loadeq}[1]{%
   \ExecuteMetaData[./equations/circuitry.tex]{eq#1}%
}

The proposed circuit in this section will perform the measurements described in the \nameref{sec:intro} and is based in part on the measurement of anodized titanium capacitors done by Ehret \cite{steve_thesis}. The circuit will measure the respones of capacitors to various test inputs in order to generate data which can then be fit to an appropriate capacitor model (Section: \ref{sec:regression}). This method will allow for an analysis of the effect of the DC bias on the output model.

This circuity provides for two main testing modes. In the first mode, a large (up to 500VDC) bias voltage is coupled onto an AC signal via an optocoupler. This voltage is then applied to the \gls{dut} and the resulting current flow is measured through a transimpedance amplifier. The signal is then filtered and its magnitude and phase are measured and digitized. The user has control of the DC bias, AC amplitude, and frequency. These control parameters can be swept to obtain a characterization of the \gls{dut}.

The second test mode provides a means to measure the discharge characteristics of the device. A DC bias is used to charge up the \gls{dut} and then disconnected. The circuity can either connect a discharge capacitor to the \gls{dut} or leave it open in order to measure the discharge current.


\nocite{my_ieeePaper}

\input{sections/circuitry/power}
\input{sections/circuitry/dcbias}
\input{sections/circuitry/opto}
\input{sections/circuitry/charge}
\input{sections/circuitry/discharge}
\input{sections/circuitry/imeas}
\input{sections/circuitry/filtering}
\input{sections/circuitry/mag}
\input{sections/circuitry/phase}
\input{sections/circuitry/adc}
\input{sections/circuitry/com}
\input{sections/circuitry/conclusion}
\input{sections/circuitry/agilent}

